---
title: "MRP vs. Traditional Norming"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	error = TRUE,
	fig.width = 8,
	fig.height = 4
)

```

Load dependencies and preprocessed datasets
```{r}
library(tidyverse)
library(ggrepel)

load("../unshareable_data/preprocessed/tl.Rda")
load("../unshareable_data/preprocessed/manual_norms.Rda")
load("data/preprocessed/census.Rda")
sim_pop_sample_with_draws <- readRDS("data/simulated/sim_pop_sample_with_draws.rds")



options(scipen = 999,
        digits = 4)

# windowsFonts(Times = windowsFont("Times New Roman"))
theme_set(theme_minimal(base_size = 12, base_family = "Times"))

# exclude first twins to avoid twin dependency issues and add variable containing the age groups from the manual
tl_no_1st_twins <- tl %>% 
 filter(ptyp != 1)

```

# MRP predictions vs. raw means

## Age group means and SDs
```{r}

means_sds_and_ses_MRP <- sim_pop_sample_with_draws %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP_mean = mean(mean_prediction), 
            MRP_se_of_mean = sd(mean_prediction), 
            MRP_sd = sqrt(mean(sd_prediction^2)), 
            MRP_se_of_sd = sd(sd_prediction)) 


means_sds_and_ses_tl <- tl_no_1st_twins %>% 
  group_by(age0100) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) %>% 
  rename(age = age0100)


means_ns_sds_and_ses <- means_sds_and_ses_MRP%>% 
  left_join(means_sds_and_ses_tl, by = "age") %>% 
  filter(age <= 65) 

# Here you can browse both MRP and raw means, SDs, and SEs.
means_ns_sds_and_ses %>% 
  mutate(age = as.integer(age)) %>% 
  DT::datatable() %>% 
  DT::formatRound(columns = names(means_ns_sds_and_ses)[-c(1, 6)], digits = 2)
```

## Plot means 

```{r}
means_ns_sds_and_ses_plot <- means_ns_sds_and_ses%>%
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")

means_ns_sds_and_ses_plot  %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(0, 5))) + 
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
    geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age == 65),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")
```

## Overall mean differences
```{r}
means_ns_sds_and_ses <- means_ns_sds_and_ses %>% 
  mutate(dif = MRP_mean - Raw_mean,
         abs_dif = abs(MRP_mean - Raw_mean))

mean(means_ns_sds_and_ses$dif)
mean(means_ns_sds_and_ses$abs_dif)
  
t.test(means_ns_sds_and_ses$Raw_mean, means_ns_sds_and_ses$MRP_mean)
```

On average an absolute difference of ~ fifth of an SD between raw and corrected means. 


## Plot SDs

```{r}
means_ns_sds_and_ses_plot %>%
  ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(0, 5))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*se_of_sd, ymax = sd + 1.96*se_of_sd), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3)) +
    geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age == 65),
    aes(label = source), family = "Times", seed = 810, nudge_x = 2, hjust = 0) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#e69f00")) +
  labs(x = "Age", y = "CFT 20-R Score SD")
```


# MRP norms vs. manual norms vs. raw estimates

Here we compare the MRP-based norms to the traditionally constructed norms reported in the CFT 20-R manual. We aggregate by the age groups as reported in the manual normal tables. Note that the manual means and SDs for ages 20 and older are based on the very same TwinLife sample we are using, they just use a different correction method that isn't described in enough detail to make it reproducible for us. 

## Means

```{r}
means_sds_and_ses_MRP <- sim_pop_sample_with_draws  %>% 
  mutate(age_group = case_when(
                         age == 11 ~ '11',
                         age == 12 ~ '12',
                         age == 13 ~ '13',
                         age == 14 ~ '14',
                         age == 15 ~ '15',
                         age == 16 ~ '16',
                         age >= 17 & age <= 19 ~ '17-19',
                         age >= 20 & age <= 24 ~ '20-24',
                         age >= 25 & age <= 29 ~ '25-29',
                         age >= 30 & age <= 34 ~ '30-34',
                         age >= 35 & age <= 39 ~ '35-39',
                         age >= 40 & age <= 44 ~ '40-44',
                         age >= 45 & age <= 49 ~ '45-49',
                         age >= 50 & age <= 54 ~ '50-54',
                         age >= 55 & age <= 59 ~ '55-59',
                         age >= 60 & age <= 64 ~ '60-64',
                         TRUE ~ NA_character_)) %>% 
  group_by(age_group, .draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MRP_mean = mean(mean_prediction),
              MRP_se_of_mean = sd(mean_prediction),
              MRP_sd = sqrt(mean(sd_prediction^2)),
              MRP_se_of_sd = sd(sd_prediction)) %>% 
  filter(!is.na(age_group))


means_sds_and_ses_tl <- tl_no_1st_twins %>% 
  filter(!is.na(age_group)) %>%
  group_by(age_group) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) 



means_sds_and_ses <- means_sds_and_ses_MRP %>%
  left_join(means_sds_and_ses_tl, by = "age_group") %>% 
  left_join(manual_norms, by = "age_group")

means_sds_and_ses_plot <- means_sds_and_ses  %>% 
  pivot_longer(-age_group, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")

# means and CIs
means_sds_and_ses_plot %>%
  ggplot(aes(x = age_group, y = mean, group = source, colour = source)) +
  scale_x_discrete(expand = expansion(add = c(0, 2))) + 
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3))  +
  scale_colour_manual(values = c("#009e73", "#0072b2", "#e69f00")) +
    geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "60-64"),
    aes(label = c("MRP", "Raw", "")), 
    family = "Times", seed = 810, nudge_x = .5, hjust = 0) + 
  labs(x = "Age Group", y = "Mean CFT 20-R Score") +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "14"),
    aes(label = c("", "", "Manual, school sample")), 
    family = "Times", seed = 810, nudge_y = 2.5) +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "40-44"),
    aes(label = c("", "", "Manual, TwinLife sample")), 
    family = "Times", seed = 810, nudge_y = -2.5) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  )  + 
  geom_vline(xintercept = 7.5)
```

## SDs
```{r}
means_sds_and_ses_plot %>%
  ggplot(aes(x = age_group, y = sd, group = source, colour = source)) +
  scale_x_discrete(expand = expansion(add = c(0, 2))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*se_of_sd, ymax = sd + 1.96*se_of_sd), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3))  +
  scale_colour_manual(values = c("#009e73", "#0072b2", "#e69f00")) +
    geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "60-64"),
    aes(label = c("MRP", "Raw", "")), 
    family = "Times", seed = 810, nudge_x = .5, hjust = 0) + 
  labs(x = "Age Group", y = "Mean CFT 20-R Score") +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "14"),
    aes(label = c("", "", "Manual, school sample")), 
    family = "Times", seed = 810, nudge_y = -.5, nudge_x = -.5) +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "40-44"),
    aes(label = c("", "", "Manual, TwinLife sample")), 
    family = "Times", seed = 810, nudge_y = .5) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) + 
  geom_vline(xintercept = 7.5) + 
  labs(x = "Age Group", y = "CFT 20-R Score SD") 
```


## IQ calculations

Rather than calculating IQs for all possible CFT 20-R scores (0-56), we restrict our calculations to those which occur in our data. 

### Linearly transformed IQs

```{r}
iq <- function(cft_score, mean, sd) {
  iq_score <- ((cft_score - mean) / sd) * 15 + 100
  return(iq_score)
}


iqs_linear <- tl_no_1st_twins %>% 
  filter(!is.na(age_group)) %>% 
  group_by(age_group, cft) %>% 
  summarise(n()) %>% 
  select(age_group, cft) %>% 
  left_join(select(means_sds_and_ses, c(Manual_mean, MRP_mean, Manual_sd, MRP_sd, age_group)), by = "age_group") %>% 
  mutate(MRP_IQ_linear = round(iq(cft, MRP_mean, MRP_sd)),
         Manual_IQ_linear = round(iq(cft, Manual_mean, Manual_sd)),
         IQ_linear_dif = MRP_IQ_linear - Manual_IQ_linear,
         IQ_linear_dif_abs = abs(MRP_IQ_linear - Manual_IQ_linear))

```

### Normalised (area transformed / normal rank transformed) IQs

```{r}
iqs_normalised <- sim_pop_sample_with_draws %>% 
  mutate(raw_score = round(.prediction),
         age_group = case_when(
                         age == 11 ~ '11',
                         age == 12 ~ '12',
                         age == 13 ~ '13',
                         age == 14 ~ '14',
                         age == 15 ~ '15',
                         age == 16 ~ '16',
                         age >= 17 & age <= 19 ~ '17-19',
                         age >= 20 & age <= 24 ~ '20-24',
                         age >= 25 & age <= 29 ~ '25-29',
                         age >= 30 & age <= 34 ~ '30-34',
                         age >= 35 & age <= 39 ~ '35-39',
                         age >= 40 & age <= 44 ~ '40-44',
                         age >= 45 & age <= 49 ~ '45-49',
                         age >= 50 & age <= 54 ~ '50-54',
                         age >= 55 & age <= 59 ~ '55-59',
                         age >= 60 & age <= 64 ~ '60-64',
                         TRUE ~ NA_character_)) %>% 
  filter(!is.na(age_group)) %>% 
  group_by(age_group, .draw) %>% 
  mutate(percentile = ecdf(raw_score)(raw_score)) %>%
  mutate(iq_score_tr_ag = qnorm(percentile) * 15 + 100) %>% 
  group_by(age_group, raw_score) %>% 
  summarise(percentile = mean(percentile),
            iq_score_tr_ag = mean(iq_score_tr_ag)) %>% 
  mutate(iq_score_tr_ag = ifelse(is.finite(iq_score_tr_ag), iq_score_tr_ag, NA),
         iq_score_ag_tr = qnorm(percentile) * 15 + 100,
         MRP_IQ_normalised = round(coalesce(iq_score_tr_ag, iq_score_ag_tr))) %>% 
  select(age_group, raw_score, MRP_IQ_normalised) %>% 
  rename("cft" = raw_score)
```

### Some aggregated comparisons between MRP and Manual IQs

```{r}
iq_table <- iqs_linear %>% 
  left_join(iqs_normalised, by = c("age_group", "cft")) %>% 
  mutate(IQ_MRP_abs_dif = abs(MRP_IQ_linear - MRP_IQ_normalised),
         Manual_kids_sample = ifelse(age_group %in% c("11", "12", "13", "14", "15", "16", "17-19"), TRUE, FALSE)) 


mean(iq_table$IQ_linear_dif_abs)

mean(iq_table$IQ_MRP_abs_dif)

iq_table %>% group_by(Manual_kids_sample) %>% summarise(mean(IQ_linear_dif_abs))
```





# Session info
```{r}
sessionInfo()
```




