---
title: "Supplementary analyses"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	error = TRUE
)

```

Load dependencies and preprocessed datasets
```{r}
library(tidyverse)
library(ggrepel)
library(kableExtra)
library(brms)
library(tidybayes)
library(marginaleffects)

load("../unshareable_data/preprocessed/tl.Rda")
load("data/preprocessed/census.Rda")


options(mc.cores = 4, 
        brms.backend = "cmdstanr",
        scipen = 999,
        digits = 4)

# windowsFonts(Times = windowsFont("Times New Roman"))
theme_set(theme_gray(base_size = 14, base_family = "Times"))

# exclude first twins to avoid twin dependency issues
tl_no_1st_twins <- tl %>% 
 filter(ptyp != 1)



```

# Multilevel model predictions without poststratification

In order to clearly see the contribution of poststratification as opposed to only making predictions based on the regression model (as is done in continuous norming and similar approaches for example), we superimposed another line for non-poststratified predictions on the plot seen in the Tutorial document. We did this using a function at an earlier stage of the project to facilitate comparing several models:

## Function for plotting MRP results and comparing them with raw values and MR predictions

```{r}
mrp_age_norms <- function(ps_table, ps_variables, brm) {

  
if ("cft_total" %in% colnames(brm$data)) {
  brm$data <- brm$data %>%
    rename(cft = cft_total)
}
  norming_sample <- brm$data
  

  
  sim_pop_sample <- ps_table %>%
  filter(census_n != 0) %>%
  ungroup() %>% 
  sample_n(size = 100000, # 67738120 is total census_n in PS table
           weight = census_n, 
           replace = TRUE) %>% 
    select(all_of(ps_variables))
  
  
  sim_pop_sample_with_draws <- sim_pop_sample %>%
  add_predicted_draws(brm, ndraws = 100, seed = 810,
                      allow_new_levels = T) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, # censor predictions which go over scale limits
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))

  
  means_sds_and_ses_MRP <- sim_pop_sample_with_draws %>%
    group_by(age, .draw) %>% 
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MRP_mean = mean(mean_prediction), 
              MRP_seOfmean = sd(mean_prediction), 
              MRP_sd = sqrt(mean(sd_prediction^2)), 
              MRP_seOfsd = sd(sd_prediction))
  
  sim_norming_sample <- brm$data %>% 
    select(all_of(ps_variables)) %>% 
    mutate(age = floor(age)) %>% 
    group_by_all() %>%
    summarise(Raw_n = n()) %>% 
    ungroup() %>% 
    sample_n(size = 100000, weight = Raw_n, replace = TRUE) 
  
  sim_norming_sample_with_draws <- sim_norming_sample %>% 
    select(all_of(ps_variables))  %>%
  add_predicted_draws(brm, ndraws = 100, seed = 810,
                      allow_new_levels = T) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, # censor predictions which go over scale limits
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))
  
  means_sds_and_ses_MR <- sim_norming_sample_with_draws %>%
    mutate(age = floor(age)) %>%
    group_by(age, .draw) %>% 
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MR_mean = mean(mean_prediction), 
              MR_seOfmean = sd(mean_prediction), 
              MR_sd = sqrt(mean(sd_prediction^2)), 
              MR_seOfsd = sd(sd_prediction))
  
  means_sds_and_ses_raw <- norming_sample  %>%
    mutate(age = floor(age)) %>%
    group_by(age) %>% 
    summarise(Raw_n = n(), 
              Raw_mean = mean(cft, na.rm = TRUE), 
              Raw_sd = sd(cft, na.rm = TRUE), 
              Raw_seOfmean = Raw_sd/sqrt(Raw_n))
  
  means_ns_sds_and_ses <- means_sds_and_ses_MRP  %>%
    left_join(means_sds_and_ses_MR, by = c("age")) %>% 
    left_join(means_sds_and_ses_raw, by = "age") 
  
  means_ns_sds_and_ses %>% 
    filter(age <= 65) %>% 
    pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") 
  
  means_plot <- means_ns_sds_and_ses %>%
  filter(age <= 65) %>%
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)")  %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*seOfmean, ymax = mean + 1.96*seOfmean), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3)) +
  geom_label_repel(
    data = means_ns_sds_and_ses %>% filter(age <= 65) %>% pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)")  %>% group_by(source) %>% filter(age == 11),
    aes(label = source, x = as.factor(age), y = mean, color = source), family = "Times", seed = 810) +
  scale_x_discrete(breaks = seq(12, 79, by = 2)) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Times"),
    legend.position = "none") +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

  
  SDs_plot <- means_ns_sds_and_ses %>%
  filter(age <= 65) %>%
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") %>%
  ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*seOfsd, ymax = sd + 1.96*seOfsd), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3)) +
  geom_label_repel(
    data = means_ns_sds_and_ses %>% filter(age <= 65) %>% pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") %>% group_by(source) %>% filter(age == 11),
    aes(label = source, x = as.factor(age), y = sd, color = source), family = "Times", seed = 810) +
  scale_x_discrete(breaks = seq(12, 79, by = 2)) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Times"),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "CFT 20-R Score SD")
  
  SEs_plot <- means_ns_sds_and_ses %>%
  filter(age <= 65) %>%
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") %>%
  filter(source != "census") %>%
  ggplot(aes(x = as.factor(age), y = seOfmean, group = source, colour = source)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3, shape = 18) +
  geom_label_repel(
    data = means_ns_sds_and_ses %>% filter(age <= 65) %>% pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") %>% group_by(source) %>% filter(age == 11),
    aes(label = source, x = as.factor(age), y = seOfmean, color = source), family = "Times", seed = 810)  +
    scale_x_discrete(breaks = seq(12, 79, by = 2)) +
    theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Times"),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "SE of Mean")
  
  
  mrp_overall_estimates <- sim_pop_sample_with_draws %>%
    filter(age <= 65) %>% 
    group_by(.draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise("MRP Mean" = mean(mean_prediction),
              "MRP SE of Mean" = sd(mean_prediction),
              "MRP SD" = sqrt(mean(sd_prediction^2)),
              "MRP SE of SD" = sd(sd_prediction))
  
  mr_overall_estimates <- sim_norming_sample_with_draws %>%
    filter(age <= 65) %>% 
    group_by(.draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise("MR Mean" = mean(mean_prediction),
              "MR SE of Mean" = sd(mean_prediction),
              "MR SD" = sqrt(mean(sd_prediction^2)),
              "MR SE of SD" = sd(sd_prediction))
  
    
  return(list(
    means_plot = means_plot,
    SDs_plot = SDs_plot,
    SEs_plot = SEs_plot,
    mrp_overall_estimates = mrp_overall_estimates,
    mr_overall_estimates = mr_overall_estimates))
}
```

## Fit/load the prediction model
```{r}
brm_age_by_educ <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      chains = 4,
      iter = 5000,
      family = gaussian(),
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_18_delta_99_5000",
      file_refit = "never",
      data = tl_no_1st_twins)

```


## Use the mrp_age_norms function
```{r, fig.width = 9}

# debug(mrp_age_norms)
mrp_age_norms(ps_table = census, 
              ps_variables = c("age", "educ", "mig", "male"),
              brm = brm_age_by_educ)
```
Besides the obvious effect that poststratification has on means, it also smoothes SD estimates and considerably reduces SEs of both means and SDs.






# One person per family

Since the TwinLife sample is composed of families, one could argue that the dependence among estimates of family members violates the i.i.d assumption and leads to underestimation of SEs. To check the robustness of our results against this violation, we ran the same MRP but with only one person chosen randomly out of each family, thus eliminating the dependency. 

## Fit/load the prediction model
```{r}
tl_no_1st_twins_1_per_fid <- tl_no_1st_twins %>%
  group_by(fid) %>%
  sample_n(1)

brm_age_by_educ_1_per_fid <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      chains = 4,
      iter = 6000,
      family = gaussian(),
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_1_per_fid",
      file_refit = "never",
      data = tl_no_1st_twins_1_per_fid) %>%
  add_criterion("loo")
```


## Compare with raw and regular MRP
```{r, fig.width = 9}
sim_pop_sample1 <- census %>% 
  sample_n(size = 100000, # total census_n in the PS table is 67738120
           weight = census_n, 
           replace = TRUE)

sim_pop_sample_with_draws1 <- sim_pop_sample1 %>%
  add_predicted_draws(brm_age_by_educ, 
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = round(case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction)))


means_sds_and_ses_MRP1 <- sim_pop_sample_with_draws1 %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP1_mean = mean(mean_prediction), 
            MRP1_se_of_mean = sd(mean_prediction), 
            MRP1_sd = sqrt(mean(sd_prediction^2)), 
            MRP1_se_of_sd = sd(sd_prediction))


sim_pop_sample2 <- census %>% 
  sample_n(size = 100000, # total census_n in the PS table is 67738120
           weight = census_n, 
           replace = TRUE)

sim_pop_sample_with_draws2 <- sim_pop_sample2 %>%
  add_predicted_draws(brm_age_by_educ_1_per_fid, 
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = round(case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction)))


means_sds_and_ses_MRP2 <- sim_pop_sample_with_draws2 %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP2_mean = mean(mean_prediction), 
            MRP2_se_of_mean = sd(mean_prediction), 
            MRP2_sd = sqrt(mean(sd_prediction^2)), 
            MRP2_se_of_sd = sd(sd_prediction))

means_sds_and_ses_tl <- tl %>% 
  group_by(age0100) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) %>% 
  rename(age = age0100)

means_ns_sds_and_ses <- means_sds_and_ses_MRP1 %>% 
  left_join(means_sds_and_ses_MRP2, by = c("age")) %>% 
  left_join(means_sds_and_ses_tl, by = "age") 


means_ns_sds_and_ses%>%
  filter(age <= 65) %>% 
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)") %>%
  filter(source != "census" & source != "abs") %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3)) +
  geom_label_repel(
    data = means_ns_sds_and_ses %>% filter(age <= 65) %>% pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)") %>% filter(source != "census" & source != "abs") %>% group_by(source) %>% filter(age == 11),
    aes(label = c("MRP, full sample", "MRP, 1 person per family", "Raw"), x = as.factor(age), y = mean, color = source), family = "Times", seed = 810) +
  scale_x_discrete(breaks = seq(12, 79, by = 2)) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.x = element_blank(),
    text = element_text(family = "Times"),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#56b4e9", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses <- means_ns_sds_and_ses %>% 
  mutate(dif_mrp_raw_abs = abs(MRP1_mean - Raw_mean),
         dif_mrp_raw = MRP1_mean - Raw_mean,
         dif_mrps_abs = abs(MRP1_mean - MRP2_mean))

mean(means_ns_sds_and_ses$dif_mrp_raw, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrp_raw_abs, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrps_abs)
```

Despite shrinking the sample size from N = 10059 to 4044, the results seem to be largely unchanged. Only the SEs increased as would be expected.



# Distribution of the simulated norm sample

## 100000 simulated N, 1000 draws, no aggregation
```{r}
set.seed(810)
sim_pop_sample <- census %>%
  filter(census_n != 0) %>%
  ungroup() %>% 
  sample_n(size = 100000, # 67738120 is total census_n in PS table
           weight = census_n, 
           replace = TRUE) %>% 
  select(-census_n)

sim_pop_sample_with_draws <- sim_pop_sample %>%
  add_predicted_draws(brm_age_by_educ, 
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))


sim_pop_sample_with_draws %>% ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black", fill = "lightblue") +
  labs(x = "CFT 20-R Score",
       y = "Frequency")
```


```{r, fig.height=100}
sim_pop_sample_with_draws %>% filter (age <65) %>% ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black")+ 
  facet_wrap(~ age, ncol = 3)
```

## 100000 simulated N, 1 draw
```{r}
set.seed(810)
sim_pop_sample <- census %>%
  filter(census_n != 0) %>%
  ungroup() %>% 
  sample_n(size = 100000, # 67738120 is total census_n in PS table
           weight = census_n, 
           replace = TRUE) %>% 
  select(-census_n)

sim_pop_sample_with_draws <- sim_pop_sample %>%
  add_predicted_draws(brm_age_by_educ, 
                      ndraws = 1, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))


sim_pop_sample_with_draws %>% ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black", fill = "lightblue") +
  labs(x = "CFT 20-R Score",
       y = "Frequency")
```


```{r, fig.height=100}
sim_pop_sample_with_draws %>% filter (age <65) %>% ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black") + 
  facet_wrap(~ age, ncol = 3)
```





## 100000 simulated N, 1000 draws, group_by(.row)
```{r}
set.seed(810)
sim_pop_sample <- census %>%
  filter(census_n != 0) %>%
  ungroup() %>% 
  sample_n(size = 100000, # 67738120 is total census_n in PS table
           weight = census_n, 
           replace = TRUE) %>% 
  select(-census_n) 

sim_pop_sample_with_draws <- sim_pop_sample %>%
  add_predicted_draws(brm_age_by_educ, 
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))

sim_pop_sample_with_draws %>%
  mutate(age_group = case_when(
    age >= 11 & age <= 20 ~ "11-20",
    age >= 21 & age <= 50 ~ "21-50",
    age > 50  ~ ">50")) %>%
  group_by(.row, age_group) %>%
  summarise(.prediction = mean(.prediction)) %>%
  ggplot(aes(x = .prediction, fill = factor(age_group))) +
  geom_histogram(binwidth = 1, color = "black", position = "stack") +
  labs(x = "CFT 20-R Score",
       y = "Frequency")





```

```{r}
sim_pop_sample_with_draws  %>%
  group_by(.row, educ) %>%
  summarise(.prediction = mean(.prediction)) %>%  
  ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black", fill = "lightblue") +
  labs(x = "CFT 20-R Score",
       y = "Frequency") + 
  facet_wrap(~ educ, ncol = 3, scale = "free_y")
```




```{r}
sim_pop_sample_with_draws  %>%
  group_by(.row) %>%
  summarise(.prediction = mean(.prediction)) %>% 
  ggplot(aes(x = .prediction, fill = factor(educ))) +
  geom_histogram(binwidth = 1, color = "black", position = "stack") +
  labs(x = "CFT 20-R Score",
       y = "Frequency")
```





```{r}
sim_pop_sample_with_draws  %>% 
  group_by(.row) %>% 
  summarise(mean_prediction = mean(.prediction), 
            se_pred = sd(.prediction)) %>% 
  mutate(d = mean_prediction/se_pred) %>% ggplot(aes(x = d)) +
  geom_histogram(binwidth = .2, color = "black", fill = "lightblue") +
  labs(x = "CFT 20-R Score",
       y = "Frequency")
```



```{r, fig.height=100}
sim_pop_sample_with_draws %>% filter (age <65) %>% ggplot(aes(x = .prediction)) +
  geom_histogram(binwidth = 1, color = "black")+ 
  facet_wrap(~ age, ncol = 3)
```




# Session info
```{r}
sessionInfo()
```













