---
title: "Supplementary analyses"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	error = TRUE,
	fig.width = 8,
	fig.height = 4
)

```

Load dependencies and preprocessed datasets
```{r}
library(tidyverse)
library(ggrepel)
library(brms)
library(tidybayes)



load("../unshareable_data/preprocessed/tl.Rda")
load("data/preprocessed/census.Rda")
sim_pop_sample_with_draws <- readRDS("data/simulated/sim_pop_sample_with_draws.rds")


options(mc.cores = 4,
        brms.backend = "cmdstanr")

options(scipen = 999,
        digits = 4)

# windowsFonts(Times = windowsFont("Times New Roman"))
theme_set(theme_minimal(base_size = 12, base_family = "Times"))

# exclude first twins to avoid twin dependency issues
tl_no_1st_twins <- tl %>% 
 filter(ptyp != 1)
```

# Model predictions without poststratification

In order to clearly see the contribution of poststratification as opposed to only making predictions based on the regression model (as is done in continuous norming and similar approaches for example), here we compare raw and MRP means to predictions from the regularised prediction model without poststratification (MR). We did this using a function at an earlier stage of the project to facilitate comparing several models:


## Function for plotting MRP results and comparing them with raw values and MR predictions

```{r}
mrp_age_norms <- function(ps_table, ps_variables, brm) {

  
  norming_sample <- brm$data
  

  
  sim_pop_sample <- ps_table %>%
  filter(census_n != 0) %>%
  ungroup() %>% 
  sample_n(size = 100000, # 67738120 is total census_n in PS table
           weight = census_n, 
           replace = TRUE) %>% 
    select(all_of(ps_variables))
  
  
  sim_pop_sample_with_draws <- sim_pop_sample %>%
  add_predicted_draws(brm, ndraws = 1000, seed = 810,
                      allow_new_levels = T) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, # censor predictions which go over scale limits
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))

  
  means_sds_and_ses_MRP <- sim_pop_sample_with_draws %>%
    group_by(age, .draw) %>% 
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MRP_mean = mean(mean_prediction), 
              MRP_seOfmean = sd(mean_prediction), 
              MRP_sd = sqrt(mean(sd_prediction^2)), 
              MRP_seOfsd = sd(sd_prediction))
  
  sim_norming_sample <- brm$data %>% 
    select(all_of(ps_variables)) %>% 
    mutate(age = floor(age)) %>% 
    group_by_all() %>%
    summarise(Raw_n = n()) %>% 
    ungroup() %>% 
    sample_n(size = 100000, weight = Raw_n, replace = TRUE) 
  
  sim_norming_sample_with_draws <- sim_norming_sample %>% 
    select(all_of(ps_variables))  %>%
  add_predicted_draws(brm, ndraws = 1000, seed = 810,
                      allow_new_levels = T) %>% 
  mutate(.prediction = case_when(.prediction < 0 ~ 0, # censor predictions which go over scale limits
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction))
  
  means_sds_and_ses_MR <- sim_norming_sample_with_draws %>%
    mutate(age = floor(age)) %>%
    group_by(age, .draw) %>% 
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MR_mean = mean(mean_prediction), 
              MR_seOfmean = sd(mean_prediction), 
              MR_sd = sqrt(mean(sd_prediction^2)), 
              MR_seOfsd = sd(sd_prediction))
  
  means_sds_and_ses_raw <- norming_sample  %>%
    mutate(age = floor(age)) %>%
    group_by(age) %>% 
    summarise(Raw_n = n(), 
              Raw_mean = mean(cft, na.rm = TRUE), 
              Raw_sd = sd(cft, na.rm = TRUE), 
              Raw_seOfmean = Raw_sd/sqrt(Raw_n))
  
  means_ns_sds_and_ses <- means_sds_and_ses_MRP  %>%
    left_join(means_sds_and_ses_MR, by = c("age")) %>% 
    left_join(means_sds_and_ses_raw, by = "age") %>% 
    filter(age <= 65) %>% 
    pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "(.*)_(.*)") 
  
  means_plot <- means_ns_sds_and_ses %>% 
    ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*seOfmean, ymax = mean + 1.96*seOfmean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

  
  SDs_plot <- means_ns_sds_and_ses %>% 
    ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*seOfsd, ymax = sd + 1.96*seOfsd), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "CFT 20-R Score SD")
  
  
  
  SEs_plot <- means_ns_sds_and_ses %>%
  ggplot(aes(x = as.factor(age), y = seOfmean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
    geom_line(linewidth = 1) +
    geom_point(size = 3, shape = 18) +
  geom_text(
    data = means_ns_sds_and_ses %>% filter(age == 65),
    aes(label = source), family = "Times", nudge_x = 1, hjust = 0)  +
    theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#cc79a7", "#0072b2", "#e69f00")) +
  labs(x = "Age", y = "SE of Mean")
  
  
  mrp_overall_estimates <- sim_pop_sample_with_draws %>%
    filter(age <= 65) %>% 
    group_by(.draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise("MRP Mean" = mean(mean_prediction),
              "MRP SE of Mean" = sd(mean_prediction),
              "MRP SD" = sqrt(mean(sd_prediction^2)),
              "MRP SE of SD" = sd(sd_prediction))
  
  mr_overall_estimates <- sim_norming_sample_with_draws %>%
    filter(age <= 65) %>% 
    group_by(.draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise("MR Mean" = mean(mean_prediction),
              "MR SE of Mean" = sd(mean_prediction),
              "MR SD" = sqrt(mean(sd_prediction^2)),
              "MR SE of SD" = sd(sd_prediction))
  
    
  return(list(
    means_plot = means_plot,
    SDs_plot = SDs_plot,
    SEs_plot = SEs_plot,
    mrp_overall_estimates = mrp_overall_estimates,
    mr_overall_estimates = mr_overall_estimates))
}
```

## Fit/load the prediction model
```{r}
brm_age_by_educ <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      chains = 4,
      iter = 5000,
      family = gaussian(),
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_18_delta_99_5000",
      file_refit = "never",
      data = tl_no_1st_twins)

```


## Use the mrp_age_norms function
```{r}
mrp_age_norms(ps_table = census, 
              ps_variables = c("age", "educ", "mig", "male"),
              brm = brm_age_by_educ)
```

Besides the obvious effect that poststratification has on means, it also smoothes SD estimates and considerably reduces SEs of both means and SDs.


# Poststratification without regularisation
Weighting is often undertaken using simple averages instead of model predictions. Here we apply poststratification weights we calculated based on population data and use weights provided by TwinLife and compare the results to MRP and raw data.

## Poststratification weights vs. MRP & Raw
### Ignoring empty subgroups
```{r}

means_sds_and_ses_MRP <- sim_pop_sample_with_draws %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP_mean = mean(mean_prediction), 
            MRP_se_of_mean = sd(mean_prediction), 
            MRP_sd = sqrt(mean(sd_prediction^2)), 
            MRP_se_of_sd = sd(sd_prediction)) %>%
  filter(age <= 65)



means_sds_and_ses_tl_ps <- tl_no_1st_twins %>% 
  mutate(age = age0100) %>% 
  left_join((census %>% 
               filter(age <= 65) %>% 
               mutate(PS_w = census_n/sum(census_n))), by = c("age", "male", "mig", "educ")) %>% 
  filter(age <= 65) %>%
  # set PS weights of cells that exist in the sample but not in the census to 0
  mutate(PS_w = ifelse(is.na(PS_w), 0, PS_w)) %>% 
  group_by(age) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n),
            PS_mean = weighted.mean(cft, PS_w, na.rm = T), 
            PS_sd = sqrt(weighted.mean((cft - PS_mean)^2, PS_w, na.rm = T)), 
            PS_se_of_mean = PS_sd/sqrt(Raw_n))

means_ns_sds_and_ses <- means_sds_and_ses_MRP %>% 
  left_join(means_sds_and_ses_tl_ps, by = "age")  %>%
  pivot_longer(-c(age), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses %>% 
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses 
    %>% filter(age == 65) %>% arrange(source),
    aes(label = c("MRP", "P", "Raw")), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0)  +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#b66dff", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses %>% group_by(source) %>% summarise(means = mean(mean), ses = mean(se_of_mean))
```

### Weighting by education only
```{r}
census_educ_only <- census %>% 
  group_by(educ) %>% 
  summarise(census_n = sum(census_n))  %>% 
  ungroup()


means_sds_and_ses_tl_ps <- tl_no_1st_twins %>% 
  mutate(age = age0100) %>% 
  left_join((census_educ_only 
             %>% mutate(PS_w = census_n/sum(census_n))), by = c("educ")) %>%  
  group_by(age) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n),
            P_mean = weighted.mean(cft, PS_w, na.rm = T), 
            P_sd = sqrt(weighted.mean((cft - P_mean)^2, PS_w, na.rm = T)), 
            P_se_of_mean = P_sd/sqrt(Raw_n)) %>% 
  filter(!is.na(age))

means_ns_sds_and_ses <- means_sds_and_ses_MRP %>% 
  left_join(means_sds_and_ses_tl_ps, by = "age")  %>%
  pivot_longer(-c(age), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses %>% 
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses 
    %>% filter(age == 65) %>% arrange(source),
    aes(label = c("MRP", "P", "Raw")), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0)  +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#b66dff", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses %>% group_by(source) %>% summarise(means = mean(mean), ses = mean(se_of_mean))

```


### Vs. MRP & Raw & Manual
```{r}
means_sds_and_ses_MRP <- sim_pop_sample_with_draws  %>% 
  mutate(age_group = case_when(
                         age == 11 ~ '11',
                         age == 12 ~ '12',
                         age == 13 ~ '13',
                         age == 14 ~ '14',
                         age == 15 ~ '15',
                         age == 16 ~ '16',
                         age >= 17 & age <= 19 ~ '17-19',
                         age >= 20 & age <= 24 ~ '20-24',
                         age >= 25 & age <= 29 ~ '25-29',
                         age >= 30 & age <= 34 ~ '30-34',
                         age >= 35 & age <= 39 ~ '35-39',
                         age >= 40 & age <= 44 ~ '40-44',
                         age >= 45 & age <= 49 ~ '45-49',
                         age >= 50 & age <= 54 ~ '50-54',
                         age >= 55 & age <= 59 ~ '55-59',
                         age >= 60 & age <= 64 ~ '60-64',
                         TRUE ~ NA_character_)) %>% 
  group_by(age_group, .draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(MRP_mean = mean(mean_prediction),
              MRP_se_of_mean = sd(mean_prediction),
              MRP_sd = sqrt(mean(sd_prediction^2)),
              MRP_se_of_sd = sd(sd_prediction)) %>% 
  filter(!is.na(age_group))


census_manual_age_groups <- census %>% 
  mutate(age_group = case_when(
                         age == 11 ~ '11',
                         age == 12 ~ '12',
                         age == 13 ~ '13',
                         age == 14 ~ '14',
                         age == 15 ~ '15',
                         age == 16 ~ '16',
                         age >= 17 & age <= 19 ~ '17-19',
                         age >= 20 & age <= 24 ~ '20-24',
                         age >= 25 & age <= 29 ~ '25-29',
                         age >= 30 & age <= 34 ~ '30-34',
                         age >= 35 & age <= 39 ~ '35-39',
                         age >= 40 & age <= 44 ~ '40-44',
                         age >= 45 & age <= 49 ~ '45-49',
                         age >= 50 & age <= 54 ~ '50-54',
                         age >= 55 & age <= 59 ~ '55-59',
                         age >= 60 & age <= 64 ~ '60-64',
                         TRUE ~ NA_character_)) %>% 
  group_by(age_group, male, mig, educ) %>% 
  summarise(census_n = sum(census_n))  %>% 
  ungroup() %>% 
  filter(!is.na(age_group)) 
  
load("../unshareable_data/preprocessed/manual_norms.Rda")


means_sds_and_ses_tl_ps <- tl_no_1st_twins %>% 
  left_join((census_manual_age_groups 
             %>% mutate(PS_w = census_n/sum(census_n))), by = c("age_group", "male", "mig", "educ")) %>%  
  group_by(age_group) %>% 
  mutate(PS_w = ifelse(is.na(PS_w), 0, PS_w)) %>%
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n),
            P_mean = weighted.mean(cft, PS_w, na.rm = T), 
            P_sd = sqrt(weighted.mean((cft - P_mean)^2, PS_w, na.rm = T)), 
            P_se_of_mean = P_sd/sqrt(Raw_n)) %>% 
  filter(!is.na(age_group))

means_ns_sds_and_ses_plot <- means_sds_and_ses_MRP %>% 
  left_join(means_sds_and_ses_tl_ps, by = "age_group")%>%
  left_join(manual_norms, by = "age_group") %>% 
  pivot_longer(-c(age_group), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")

means_ns_sds_and_ses_plot %>%
  ggplot(aes(x = age_group, y = mean, group = source, colour = source)) +
  scale_x_discrete(expand = expansion(add = c(0, 2))) + 
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3))  +
    geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age_group == "60-64"),
    aes(label = c(source[1:3], "")), 
    family = "Times", seed = 810, nudge_x = .5, hjust = 0) + 
  labs(x = "Age Group", y = "Mean CFT 20-R Score", ) +
  geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age_group == "14"),
    aes(label = c("", "", "", "Manual, school sample")), 
    family = "Times", seed = 810, nudge_y = 2.5) +
  geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age_group == "40-44"),
    aes(label = c("", "", "", "Manual, TwinLife sample")), 
    family = "Times", seed = 810, nudge_y = -3) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  )  + 
  geom_vline(xintercept = 7.5) +
  scale_colour_manual(values = c("#009e73", "#0072b2", "#b66dff", "#e69f00"))


```

## TwinLife Weights

Here we use the weights provided by the TwinLife panel study data custodians, described [here](https://pub.uni-bielefeld.de/record/2979229). We compare them with both raw  and MRP means.

## Get the design and non-response weights from the weights dataset
```{r}

tl_no_1st_twins_w_ws <- tl_no_1st_twins %>% 
  left_join((haven::read_dta("../unshareable_data/raw/ZA6701_weights_v7-1-0.dta") %>% 
              select(c(fid, svw0100, svw0200))), by = "fid") %>% 
  # rename the weights
  mutate(dw = svw0100, # design weights
         nrw = svw0200, # non-response weights
         dnrw = svw0100*svw0200) # total weights (both weights together)
```

## Mean differences

```{r}

means_sds_and_ses_MRP <- sim_pop_sample_with_draws %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP_mean = mean(mean_prediction), 
            MRP_se_of_mean = sd(mean_prediction), 
            MRP_sd = sqrt(mean(sd_prediction^2)), 
            MRP_se_of_sd = sd(sd_prediction)) 


means_sds_and_ses_tl <- tl_no_1st_twins_w_ws %>% 
  group_by(age0100) %>% 
  summarise(n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(n),
            DesignWeighted_mean = weighted.mean(cft, dw, na.rm = T), 
            DesignWeighted_sd = sqrt(weighted.mean((cft - DesignWeighted_mean)^2, dw, na.rm = T)), 
            DesignWeighted_se_of_mean = DesignWeighted_sd/sqrt(n),
            NonresponseWeighted_mean = weighted.mean(cft, nrw, na.rm = T), 
            NonresponseWeighted_sd = sqrt(weighted.mean((cft - NonresponseWeighted_mean)^2, nrw, na.rm = T)), 
            NonresponseWeighted_se_of_mean = NonresponseWeighted_sd/sqrt(n),
            TotalWeighted_mean       = weighted.mean(cft, dnrw, na.rm = T), 
            TotalWeighted_sd         = sqrt(weighted.mean((cft - TotalWeighted_mean)^2, dnrw, na.rm = T)),
            TotalWeighted_se_of_mean = TotalWeighted_sd/sqrt(n)) %>% 
  rename(age = age0100)

means_ns_sds_and_ses <- means_sds_and_ses_MRP %>% 
  left_join(means_sds_and_ses_tl, by = "age") %>%
  filter(age <= 65) %>%
  pivot_longer(-c(age, n), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")
```



```{r}
means_ns_sds_and_ses  %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = c("Design weighted", "MRP", "Non-response weighted", "Raw", "Total weighted")), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#490092", "#0072b2", "#920000","#e69f00","#24ff24")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")
```

No large differences to raw means but it's hard to see details.



```{r}
means_ns_sds_and_ses %>%
  group_by(source) %>% 
  summarise(mean = mean(mean, na.rm = TRUE)) %>% 
  arrange(mean)
```
Overall, non response weighting also recognised an overestimation and corrected for it, but not  as much as MRP.


Since the previous plot was too cluttered, here's one with non-response only since it's the one that seems to make the largest difference to raw means.
```{r}
means_ns_sds_and_ses %>%
  filter(source != "DesignWeighted" & source != "TotalWeighted") %>% 
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text(
    data = means_ns_sds_and_ses 
    %>% filter(source != "DesignWeighted" & source != "TotalWeighted")
    %>% filter(age == 65),
    aes(label = c("MRP", "Raw", "Non-response weighted")), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0)  +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#920000", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")
```


## SD differences

```{r}
means_ns_sds_and_ses %>%
  ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*se_of_sd, ymax = sd + 1.96*se_of_sd), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = c("Design weighted", "MRP", "Non-response weighted", "Raw", "Total weighted")), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#490092", "#0072b2", "#920000","#e69f00","#24ff24")) +
  labs(x = "Age", y = "CFT 20-R Score SD")
```

```{r}
means_ns_sds_and_ses %>%
  group_by(source) %>% 
  summarise(sd = sqrt(mean(sd^2))) %>% 
  arrange(sd)
```

No large differences in SDs.


# Including first twins
Our main analysis exludes 1st twins to avoid having to deal with the twins' dependent observations and because we used the data of the 1st twins extensively for model comparison. Here we test our results' robustsness against including them.

## Fit/load the prediction model
```{r}
brm_age_by_educ_with_1st_twins <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      family = gaussian(),
      chains = 4,
      iter = 5000,
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_18_delta_99_5000_with_1st_twins",
      file_refit = "never",
      data = tl) %>% 
  add_criterion("loo")
```


## Compare with raw and regular MRP
```{r}

means_sds_and_ses_MRP1 <- sim_pop_sample_with_draws %>% # the one generated in the tutorial
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP1_mean = mean(mean_prediction), 
            MRP1_se_of_mean = sd(mean_prediction), 
            MRP1_sd = sqrt(mean(sd_prediction^2)), 
            MRP1_se_of_sd = sd(sd_prediction))


sim_pop_sample2 <- census %>% 
  sample_n(size = 100000, 
           weight = census_n, 
           replace = TRUE)

sim_pop_sample_with_draws2 <- sim_pop_sample2 %>% 
  add_predicted_draws(brm_age_by_educ_with_1st_twins, # based on the 1/family model
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = round(case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction)))


means_sds_and_ses_MRP2 <- sim_pop_sample_with_draws2 %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP2_mean = mean(mean_prediction), 
            MRP2_se_of_mean = sd(mean_prediction), 
            MRP2_sd = sqrt(mean(sd_prediction^2)), 
            MRP2_se_of_sd = sd(sd_prediction))

means_sds_and_ses_tl <- tl %>% 
  group_by(age0100) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) %>% 
  rename(age = age0100)

means_ns_sds_and_ses <- means_sds_and_ses_MRP1 %>% 
  left_join(means_sds_and_ses_MRP2, by = c("age")) %>% 
  left_join(means_sds_and_ses_tl, by = "age") %>%
  filter(age <= 65) 

means_ns_sds_and_ses_plot <- means_ns_sds_and_ses %>% 
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses_plot %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses_plot %>%  filter(age == 65) %>% arrange(source),
    aes(label = c("MRP, excl. 1st twins", "MRP, incl. 1st twins", "Raw")), family = "Times", seed = 810, nudge_x = 1, hjust = 0) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#000000", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses <- means_ns_sds_and_ses %>% 
  mutate(dif_mrp_raw_abs = abs(MRP1_mean - Raw_mean),
         dif_mrp_raw = MRP1_mean - Raw_mean,
         dif_mrps = MRP1_mean - MRP2_mean,
         dif_mrps_abs = abs(MRP1_mean - MRP2_mean))

mean(means_ns_sds_and_ses$dif_mrp_raw, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrp_raw_abs, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrps)
mean(means_ns_sds_and_ses$dif_mrps_abs)
```
# One person per family

Since the TwinLife sample is composed of families, one could argue that the dependence among estimates of family members violates the i.i.d assumption and leads to underestimation of SEs. To check the robustness of our results against this violation, we ran the same MRP but with only one person chosen randomly out of each family, thus eliminating the dependency. 

## Fit/load the prediction model
```{r}

set.seed(14)

tl_no_1st_twins_1_per_fid <- tl_no_1st_twins %>%
  group_by(fid) %>%
  sample_n(1)

brm_age_by_educ_1_per_fid <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      chains = 4,
      iter = 6000,
      family = gaussian(),
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_1_per_fid",
      file_refit = "never",
      data = tl_no_1st_twins_1_per_fid) %>%
  add_criterion("loo")
```


## Compare with raw and regular MRP
```{r}

means_sds_and_ses_MRP1 <- sim_pop_sample_with_draws %>% # the one generated in the tutorial
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP1_mean = mean(mean_prediction), 
            MRP1_se_of_mean = sd(mean_prediction), 
            MRP1_sd = sqrt(mean(sd_prediction^2)), 
            MRP1_se_of_sd = sd(sd_prediction))


sim_pop_sample2 <- census %>% 
  sample_n(size = 100000, 
           weight = census_n, 
           replace = TRUE)

sim_pop_sample_with_draws2 <- sim_pop_sample2 %>% 
  add_predicted_draws(brm_age_by_educ_1_per_fid, # based on the 1/family model
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = round(case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction)))


means_sds_and_ses_MRP2 <- sim_pop_sample_with_draws2 %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP2_mean = mean(mean_prediction), 
            MRP2_se_of_mean = sd(mean_prediction), 
            MRP2_sd = sqrt(mean(sd_prediction^2)), 
            MRP2_se_of_sd = sd(sd_prediction))

means_sds_and_ses_tl <- tl_no_1st_twins_1_per_fid %>% 
  group_by(age0100) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) %>% 
  rename(age = age0100)

means_ns_sds_and_ses <- means_sds_and_ses_MRP1 %>% 
  left_join(means_sds_and_ses_MRP2, by = c("age")) %>% 
  left_join(means_sds_and_ses_tl, by = "age") %>% 
  filter(age <= 65)

means_ns_sds_and_ses_plot <- means_ns_sds_and_ses %>% 
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses_plot %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text(
    data = means_ns_sds_and_ses_plot %>% filter(age == 65),
    aes(label = c("MRP, full sample", "MRP, 1 person/family", "Raw")),
    family = "Times", nudge_x = 1, hjust = 0) +
  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#56b4e9", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses <- means_ns_sds_and_ses %>% 
  mutate(dif_mrp_raw_abs = abs(MRP1_mean - Raw_mean),
         dif_mrp_raw = MRP1_mean - Raw_mean,
         dif_mrps = MRP1_mean - MRP2_mean,
         dif_mrps_abs = abs(MRP1_mean - MRP2_mean))

mean(means_ns_sds_and_ses$dif_mrp_raw, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrp_raw_abs, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrps)
mean(means_ns_sds_and_ses$dif_mrps_abs)
```

Despite shrinking the sample size from N = 10059 to 4044, the results seem to be largely unchanged. Only the SEs slightly increased as would be expected.



# Excluding participants with ambivalent educational attainment category

Some participants were assigned an education category that combines two degrees with variable ISCED levels: "university of applied sciences, university of cooperative education". While a degree from a university of applied sciences (Fachhochschule) would put one in ISCED level 5a, a degree from a university of cooperative education (Berufsakademie) is equivalent to ISCED level 5b. TwinLife assigns all people who have this ambivalent category to ISCED 5a. Here we test the robustness of our results against excluding those 357 participants.


## Fit/load the prediction model
```{r}

tl_no_1st_twins_no_berufsakad_with_fachhochschule <- tl_no_1st_twins %>% 
  filter(!(eca0108 == "level 5a" & eca0230 == 8))


brm_age_by_educ_modif_isced5a <-
  brm(bf(
      cft ~ (1 | mig)  + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age, by = educ),
      sigma ~ (1 | mig) + (1 | educ) + (male)  + (1 | mig:male) + (1 | mig:educ) + (1 | male:educ) + (1 | mig:educ:male) + s(age)),
      family = gaussian(),
      chains = 4,
      iter = 5000,
      seed = 810,
      control = list(adapt_delta = 0.99),
      file = "../unshareable_data/brms/brm_age_by_educ_18_delta_99_5000_isced5a",
      file_refit = "never",
      data = tl_no_1st_twins_no_berufsakad_with_fachhochschule) %>% 
  add_criterion("loo")
```


## Compare with raw and regular MRP
```{r}

means_sds_and_ses_MRP1 <- sim_pop_sample_with_draws %>% # the one generated in the tutorial
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP1_mean = mean(mean_prediction), 
            MRP1_se_of_mean = sd(mean_prediction), 
            MRP1_sd = sqrt(mean(sd_prediction^2)), 
            MRP1_se_of_sd = sd(sd_prediction))


sim_pop_sample2 <- census %>% 
  sample_n(size = 100000, 
           weight = census_n, 
           replace = TRUE)

sim_pop_sample_with_draws2 <- sim_pop_sample2 %>% 
  add_predicted_draws(brm_age_by_educ_modif_isced5a, # based on the 1/family model
                      ndraws = 1000, 
                      seed = 810, 
                      allow_new_levels = TRUE) %>% 
  mutate(.prediction = round(case_when(.prediction < 0 ~ 0, 
                                 .prediction > 56 ~ 56,
                                 TRUE ~ .prediction)))


means_sds_and_ses_MRP2 <- sim_pop_sample_with_draws2 %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(MRP2_mean = mean(mean_prediction), 
            MRP2_se_of_mean = sd(mean_prediction), 
            MRP2_sd = sqrt(mean(sd_prediction^2)), 
            MRP2_se_of_sd = sd(sd_prediction))

means_sds_and_ses_tl <- tl_no_1st_twins_no_berufsakad_with_fachhochschule %>% 
  group_by(age0100) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) %>% 
  rename(age = age0100)

means_ns_sds_and_ses <- means_sds_and_ses_MRP1 %>% 
  left_join(means_sds_and_ses_MRP2, by = c("age")) %>% 
  left_join(means_sds_and_ses_tl, by = "age") %>% 
  filter(age <= 65)

means_ns_sds_and_ses_plot <- means_ns_sds_and_ses %>% 
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses_plot %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(12, 64, by = 2),
                   expand = expansion(add = c(1, 15))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses_plot %>% filter(age == 65) %>% arrange(source),
    aes(label = c("MRP, full sample", "MRP, no BeAk/FHS", "Raw")), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c("#0072b2", "#924900", "#e69f00")) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

means_ns_sds_and_ses <- means_ns_sds_and_ses %>% 
  mutate(dif_mrp_raw_abs = abs(MRP1_mean - Raw_mean),
         dif_mrp_raw = MRP1_mean - Raw_mean,
         dif_mrps = MRP1_mean - MRP2_mean,
         dif_mrps_abs = abs(MRP1_mean - MRP2_mean))

mean(means_ns_sds_and_ses$dif_mrp_raw, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrp_raw_abs, na.rm=T)
mean(means_ns_sds_and_ses$dif_mrps)
mean(means_ns_sds_and_ses$dif_mrps_abs)
```




# Session info
```{r}
sessionInfo()
```













