---
title: "RPP vs. Alternative norming methods"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	error = TRUE,
	fig.width = 8,
	fig.height = 4
)


library(tidyverse)
library(haven)
library(ggrepel)
library(kableExtra)
library(rstan)
library(kableExtra)





options(scipen = 999,
        digits = 4)

theme_set(theme_minimal(base_size = 12, base_family = "Times"))

load("../../unshareable_data/preprocessed/tl.Rda")
load("../../unshareable_data/preprocessed/manual_norms.Rda")
load("../01_data/preprocessed/de_census/census.Rda")
load("../01_data/preprocessed/de_census/census_margins.Rda")

source("age_norm_comparisons.R")
```




# RPP predictions vs. raw means
## Compare sample to population demographics
### Marginal
One plot for age and one for the three other variables.

```{r}
# Custom sorting function
custom_sort <- function(x) {
  st_categories <- x[startsWith(x, "ST")]
  isced_categories <- x[startsWith(x, "ISCED")]
  other_categories <- x[!startsWith(x, "ST") & !startsWith(x, "ISCED")]
  
  factor(x, levels = c(sort(st_categories), sort(isced_categories), other_categories))
}

# get the marginal distributions from the census and the TL sample

disparities_plot <- census %>% 
  full_join(tl %>% 
  group_by(age = age0100, male, educ, mig) %>% 
  summarise(sample_n = n()) %>% 
  mutate(sample_n = as.numeric(sample_n)), by = c("age", "male", "educ", "mig")) %>% 
  mutate(sample_n = replace_na(sample_n, 0)) %>%
  pivot_longer(cols = c(census_n:sample_n), names_to = "source", values_to = "n") %>% 
  mutate(age = as.character(age),
         male = as.character(male),
         source = str_sub(source, 1, -3)) %>% 
pivot_longer(cols = -c(n, source), names_to = "variable", values_to = "category") %>% 
  group_by(source, variable, category) %>% 
  summarise(n = sum(n)) %>% 
  mutate(percentage = n/sum(n)*100) %>% 
  filter(source == "sample") %>% 
  bind_rows(census_margins) %>%
  mutate(category = case_when(
    category == "TRUE" ~ "Male",
    category == "FALSE" ~ "Female",
    TRUE ~ category)) %>% 
  mutate(category = custom_sort(category))

# plot age disparities
disparities_plot %>%
  filter(variable == "age") %>%
  ggplot(aes(x = category, y = percentage, group = source, colour = source, label = round(percentage, digits = 1))) +
  geom_line(linewidth = 1) +
  facet_grid(cols = vars(variable), scales = "free", space = 'free', as.table = FALSE,
             labeller = labeller(variable = function(variable) {
               case_when(
                 variable == "age" ~ "Age",
                 TRUE ~ as.character(variable))})) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = c(1, 1.08),  #
        legend.justification = c(1, 1), 
        legend.background = element_rect(fill = "transparent", color = NA),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linewidth = 0.3, linetype = "dashed")) +  # Changed size to linewidth
  labs(x = "Category", y = "Percentage", colour = "", label = "Percentage") +
  scale_colour_manual(values = c("#0072B5FF", "#BC3C29FF"), labels = function(x) str_to_title(x)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2))

ggsave("../04_figures/02_disparities_age.png", width = 8, height = 4)
```


```{r}
disparities_plot %>%
  filter(variable != "age") %>%
  ggplot(aes(x = category, y = percentage, group = source, colour = source, label = round(percentage, digits = 1))) +
  geom_line(linewidth = 1) +
  # theme_minimal(base_size = 14, base_family = "Times") +
  facet_grid(
    cols = vars(variable),
    scales = "free",
    space = 'free',
    as.table = FALSE,
    labeller = labeller(variable = function(variable) {
      case_when(
        variable == "educ" ~ "School Type / ISCED 1997 Code",
        variable == "male" ~ "Sex",
        variable == "mig" ~ "Migration",
        TRUE ~ as.character(variable))})) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = c(1, 1.1),  #
        legend.justification = c(1, 1), 
        legend.background = element_rect(fill = "transparent", color = NA),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linetype = "dashed", linewidth = 0.3)) +  # Changed size to linewidth
  labs(x = "Category", y = "Percentage", colour = "", label = "Percentage") +
  scale_colour_manual(values = c("#0072B5FF", "#BC3C29FF"), labels = function(x) str_to_title(x)) +
  geom_text_repel(family = "Times", seed = 14, point.padding = 2, direction = "y", hjust = 0)

ggsave("../04_figures/02_disparities_other_vars.png", width = 8, height = 4)
```

Besides the obvious age disparities due to the cohort design adopted to collect the data for the TwinLife sample, we also see that our sample is "overeducated" in the sense that for example we have too many kids who were going to the Gymnasium (ST4: upper secondary) and too few adults who have something similar to an Ausbildungsabschluss (ISCED 3b: upper secondary, vocational). Migrants and females are also overrepresented in the sample. 


### Joint

You can use this interactive table to browse disparities at the level of joint distributions, ordered after magnitude. Note that this table has 5184 rows (number of subgroups/combinations of the 4 variables we use). Most of these subgroups are empty in the sample. 


```{r}
census %>% 
  full_join(tl %>% 
  group_by(age0100, male, educ, mig) %>% 
  summarise(sample_n = n()) %>% 
  rename(age = "age0100") %>% 
  mutate(sample_n = as.numeric(sample_n)), by = c("age", "male", "educ", "mig")) %>% 
  # set the subgroups which are empty in the sample to 0 instead of NA
  mutate(sample_n = replace_na(sample_n, 0)) %>% 
  group_by(age, male, educ, mig) %>% 
  summarise(census_n = sum(census_n),
            sample_n = sum(sample_n)) %>% 
  group_by(age) %>% 
  mutate(census_percentage = census_n*100/sum(census_n),
         sample_percentage = sample_n*100/sum(sample_n),
         dif_percentage = census_percentage-sample_percentage,
         relative_dif = dif_percentage*census_n/100,
         age = as.integer(age)) %>% 
  relocate(census_percentage, .after = "census_n") %>%
  arrange(-relative_dif) %>% DT::datatable() %>% 
  DT::formatRound(c('dif_percentage', 'relative_dif', 'census_percentage', 'sample_percentage'), digits = 1)
```

## Age group means, SDs, and SEs

```{r}
RPP_vs_raw <- age_norm_comparisons(
  brm_MAIN_skew_s_by_educ_mig_male_int, 
  ps_table = census, 
  # RP = c("census", "norming_sample"),
  ps_variables = c("age", "educ", "mig", "male"), 
  re_formula = NULL,
  sim_size = 100000,
  labels = c( "Raw", "RPP"),
   palette = c(
  "#BC3C29FF",
  "#0072B5FF"
),  
  output_file = "../01_data/results/RPP_vs_raw.rds"
  )

RPP_vs_raw[-1]
```


```{r}
RPP_vs_raw$means_plot <- RPP_vs_raw$means_plot + 
  scale_x_continuous(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(0, 2)))
ggsave("../04_figures/04_RPP_vs_raw_vs_RP.png", RPP_vs_raw$means_plot, width = 8, height = 4)

RPP_vs_raw$SDs_plot <- RPP_vs_raw$SDs_plot + 
  scale_x_continuous(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(0, 2)))


ggsave("../04_figures/05_RPP_vs_raw_vs_RP.png", RPP_vs_raw$SDs_plot, width = 8, height = 4)
```


## Overall mean differences
```{r}
RPP_vs_raw$overall_estimates$Mean - mean(tl$cft)


RPP_vs_raw$means_ns_sds_and_ses %>% pivot_wider(names_from = source, names_sep = "_", values_from = -age) %>% 
  mutate(dif = mean_RPP - mean_Raw,
         abs_dif = abs(mean_RPP - mean_Raw)) %>% 
  summarise(mean(dif), mean(abs_dif))
```

On average an absolute difference of ~ fifth of an SD between raw and corrected means. 


# RPP norms vs. manual norms vs. raw estimates

Here we compare the RPP-based norms to the traditionally constructed norms reported in the CFT 20-R manual. We aggregate by the age groups as reported in the manual normal tables. Note that the manual means and SDs for ages 20 and older are based on the very same TwinLife sample we are using, they just use a different correction method that isn't described in enough detail to make it reproducible for us. 

## Means

```{r}
sim_pop_sample_with_draws <- data.table::fread("../01_data/results/sim_pop_sample_with_draws.csv.gz")

means_sds_and_ses_RPP <- sim_pop_sample_with_draws %>% 
  group_by(age_group, .draw) %>%
    summarise(mean_prediction = mean(.prediction), sd_prediction = sd(.prediction)) %>%
    summarise(RPP_mean = mean(mean_prediction),
              RPP_se_of_mean = sd(mean_prediction),
              RPP_sd = sqrt(mean(sd_prediction^2)),
              RPP_se_of_sd = sd(sd_prediction)) 



means_sds_and_ses_tl <- tl %>% 
  filter(!is.na(age_group)) %>%
  group_by(age_group) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n)) 



means_sds_and_ses <- means_sds_and_ses_RPP %>%
  left_join(means_sds_and_ses_tl, by = "age_group") %>% 
  left_join(manual_norms, by = "age_group") %>% 
  filter(!is.na(Raw_n))

means_sds_and_ses_plot <- means_sds_and_ses  %>% 
  pivot_longer(-age_group, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")

# means and CIs
means_sds_and_ses_plot %>%
  ggplot(aes(x = age_group, y = mean, group = source, colour = source)) +
  scale_x_discrete(expand = expansion(add = c(0, 2))) + 
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3))  +
  scale_colour_manual(values = c("#20854EFF", "#BC3C29FF", "#0072B5FF")) +
    geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "60-64"),
    aes(label = c("RPP", "Raw", "")), 
    family = "Times", seed = 810, nudge_x = .5, hjust = 0) + 
  labs(x = "Age Group", y = "Mean CFT 20-R Score") +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "14"),
    aes(label = c("", "", "Manual, school sample")), 
    family = "Times", seed = 810, nudge_y = 2.5) +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "40-44"),
    aes(label = c("", "", "Manual, TwinLife sample")), 
    family = "Times", seed = 810, nudge_y = -2.5) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  )  + 
  geom_vline(xintercept = 7.5)

ggsave("../04_figures/06_vs_Manual_means.png", width = 8, height = 4)
```

## SDs
```{r}
means_sds_and_ses_plot %>%
  ggplot(aes(x = age_group, y = sd, group = source, colour = source)) +
  scale_x_discrete(expand = expansion(add = c(0, 2))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*se_of_sd, ymax = sd + 1.96*se_of_sd), 
                  fatten = 6,
                  linewidth = 1.5,
                  position = position_dodge(width = 0.3))  +
  scale_colour_manual(values = c("#20854EFF", "#BC3C29FF", "#0072B5FF")) +
    geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "60-64"),
    aes(label = c("RPP", "Raw", "")), 
    family = "Times", seed = 810, nudge_x = .5, hjust = 0) + 
  labs(x = "Age Group", y = "Mean CFT 20-R Score") +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "14"),
    aes(label = c("", "", "Manual, school sample")), 
    family = "Times", seed = 810, nudge_y = -.5, nudge_x = -.5) +
  geom_text_repel(
    data = means_sds_and_ses_plot %>% filter(age_group == "40-44"),
    aes(label = c("", "", "Manual, TwinLife sample")), 
    family = "Times", seed = 810, nudge_y = .5) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) + 
  geom_vline(xintercept = 7.5) + 
  labs(x = "Age Group", y = "CFT 20-R Score SD")

ggsave("../04_figures/07_vs_Manual_SDs.png", width = 8, height = 4)
```



## IQ calculations

Rather than calculating IQs for all possible CFT 20-R scores (0-56), we restrict our calculations to those which occur in our data.

### Linearly transformed IQs

```{r}
iq <- function(cft_score, mean, sd) {
  iq_score <- ((cft_score - mean) / sd) * 15 + 100
  return(iq_score)
}


iqs_linear <- tl %>% 
  filter(!is.na(age_group)) %>% 
  select(age_group, raw_score = cft) %>% 
  left_join(means_sds_and_ses, by = "age_group") %>%
  group_by(age_group) %>% 
  mutate(RPP_IQ_linear = iq(raw_score, RPP_mean, RPP_sd),
         Manual_IQ_linear = iq(raw_score, Manual_mean, Manual_sd)) %>% 
  group_by(age_group, raw_score) %>% 
  summarise(RPP_IQ_linear = round(mean(RPP_IQ_linear)),
            Manual_IQ_linear = round(mean(Manual_IQ_linear)),
            IQ_linear_dif = RPP_IQ_linear - Manual_IQ_linear,
            IQ_linear_dif_abs = abs(RPP_IQ_linear - Manual_IQ_linear))
  
```


### Normalised (area transformed / normal rank transformed) IQs

```{r}
iqs_normalised <- sim_pop_sample_with_draws %>%
  filter(!is.na(age_group)) %>%
  group_by(age_group, .draw) %>%
  mutate(n = n(),
         normal_transformed_score = qnorm((rank(.prediction) - 0.5) / n)) %>%
  mutate(iq_score = normal_transformed_score * 15 + 100) %>%
  group_by(age_group, raw_score = .prediction) %>%
  summarise(RPP_IQ_normalised = round(mean(iq_score)),
            RPP_IQ_normalised_se = sd(iq_score))
```

### Some aggregated comparisons between RPP and Manual IQs

```{r}
iq_table <- iqs_linear %>% 
  left_join(iqs_normalised, by = c("age_group", "raw_score")) %>% 
  mutate(IQ_RPP_abs_dif = abs(RPP_IQ_linear - RPP_IQ_normalised),
         Manual_kids_sample = ifelse(age_group %in% c("11", "12", "13", "14", "15", "16", "17-19"), TRUE, FALSE)) 


mean(iq_table$IQ_linear_dif_abs)
max(iq_table$IQ_linear_dif_abs)
mean(iq_table$IQ_RPP_abs_dif)

iq_table %>% group_by(Manual_kids_sample) %>% summarise(mean(IQ_linear_dif_abs))
```

### Selection of 9 IQs
```{r}
t <- tibble("Manual Normalised IQ" = c(62, 92, 135, 70, 97, 134, 76, 100, 130))

iq_table %>% 
  select(age_group, raw_score, "RPP Normalised IQ" = RPP_IQ_normalised, "RPP Linear IQ" = RPP_IQ_linear, "Manual Linear IQ" = Manual_IQ_linear) %>% 
  filter((age_group == "16" & raw_score %in% c(22, 37, 53)) |
         (age_group == "30-34" & raw_score %in% c(19, 37, 52)) |
         (age_group == "60-64" & raw_score %in% c(12, 30, 46))) %>% 
  bind_cols(t) %>% 
  relocate("Manual Normalised IQ", .before = "RPP Linear IQ") %>% 
    kable()
```



# RPP norms vs. continuous norming + raking
## Fit cNorm model
Following the vignette [here](https://cran.r-project.org/web/packages/cNORM/vignettes/WeightedRegression.html).

```{r, warning=TRUE}
library(cNORM)

## Norm sample

norm.data <- tl %>% select(age = age0100, educ, male, mig, cft) %>% 
  as.data.frame() %>% mutate(age = as.numeric(age))


## Generate population margins
load("../01_data/preprocessed/de_census/census_margins.Rda")


# Both dfs have to be class `data.frame`, `tibble` is no-go.
margins <- as.data.frame(census_margins %>%
  mutate(var = variable,
         level = category,
         prop = percentage/100) %>% 
  select(var, level, prop))


## Calculate raking weights
weights <- computeWeights(data = norm.data, population.margins = margins)


## Norming model
norm.model <- cnorm(raw = norm.data$cft,
                    group = norm.data$age,
                    weights = weights,
                    scale = "IQ")

summary(norm.model)
```


## Extract IQ predictions and compare results

```{r}
# get means and sds for calculating iqs
means_sds_and_ses_RPP <- sim_pop_sample_with_draws %>%
  group_by(age) %>% 
  summarise(RPP_mean = mean(.prediction), 
            RPP_sd = sd(.prediction)) 

```

### For the sample on which the models were fit.
```{r}

iqs_norming_sample <- norm.data %>% 
  select(age, raw_score = cft) %>% 
  left_join(means_sds_and_ses_RPP, by = "age") %>%
  group_by(age) %>%
  mutate(RPP_IQ_linear = iq(raw_score, RPP_mean, RPP_sd),
         cNorm_IQ = predictNorm(raw = raw_score, 
                                A = age,
                                model = norm.model),
         dif = RPP_IQ_linear - cNorm_IQ,
         absolute_dif = abs(RPP_IQ_linear - cNorm_IQ)) %>% 
  ungroup()

# overall_comparison 
iqs_norming_sample  %>% 
  summarise(mean_RPP_IQ = mean(RPP_IQ_linear),
            mean_cNorm_IQ = mean(cNorm_IQ),
            mean_dif = mean(dif),
            max_dif = max(dif),
            mean_absolute_dif = mean(absolute_dif),
            RMS_dif = sqrt(mean(dif^2))) %>% kable()


```


### For a random sample from the poststratified simulated sample
```{r}

iqs_random_sample <- sim_pop_sample_with_draws %>%  
  group_by(.row) %>%
  slice(1) %>%
  select(age, raw_score = .prediction) %>% 
  left_join(means_sds_and_ses_RPP, by = "age") %>%
  group_by(age) %>%
  mutate(RPP_IQ_linear = iq(raw_score, RPP_mean, RPP_sd),
         cNorm_IQ = predictNorm(raw = raw_score, 
                                A = age,
                                model = norm.model),
         dif = RPP_IQ_linear - cNorm_IQ,
         absolute_dif = abs(RPP_IQ_linear - cNorm_IQ)) %>% 
  ungroup()


# overall_comparison 
iqs_random_sample %>% 
  summarise(mean_RPP_IQ = mean(RPP_IQ_linear),
            mean_cNorm_IQ = mean(cNorm_IQ),
            mean_dif = mean(dif),
            max_dif = max(dif),
            mean_absolute_dif = mean(absolute_dif),
            RMS_dif = sqrt(mean(dif^2))) %>% kable()


```



### Plots
#### Age group IQs based on the norming sample
```{r}
means_ns_sds_and_ses <- iqs_norming_sample %>% 
  group_by(age) %>% 
  summarise(RPP_mean = mean(RPP_IQ_linear),
            RPP_sd = sd(RPP_IQ_linear),
            cNorm_mean = mean(cNorm_IQ),
            cNorm_sd = sd(cNorm_IQ)) %>% 
  pivot_longer(-age, names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses  %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(1, 5))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean , ymax = mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c(
  "#E18727FF",
  "#0072B5FF"

)) +
  labs(x = "Age", y = "IQ")

ggsave("../04_figures/08_RPP_vs_cNorm.png", width = 8, height = 4)
```

```{r}
means_ns_sds_and_ses  %>%
  ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(1, 5))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd , ymax = sd), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c(
  "#E18727FF",
  "#0072B5FF"

)) +
  labs(x = "Age", y = "SD")
```



#### Mean difference, mean absolute difference, and RMS difference  
```{r}
# Put them in a named list
df_list <- list(
  "Norming sample"   = iqs_norming_sample,
  "Simulated poststratified sample"     = iqs_random_sample
)

# Create a single table with all results
combined <- df_list %>%
  imap_dfr(~ {
    # .x is the data frame, .y is the name in the list (e.g. "norming_sample")
    
    # 1) No tail filtering:
    no_filter <- .x %>%
      summarise(
        mean_dif          = mean(dif),
        mean_absolute_dif = mean(absolute_dif),
        RMS_dif           = sqrt(mean(dif^2))
      ) %>%
      pivot_longer(
        cols      = everything(),
        names_to  = "value_type",
        values_to = "value"
      ) %>%
      mutate(
        at_tails = FALSE,
        source   = .y
      )
    
    # 2) With tail filtering:
    with_filter <- .x %>%
      filter(between(RPP_IQ_linear, 65, 75) | between(RPP_IQ_linear, 125, 135)) %>%
      summarise(
        mean_dif          = mean(dif),
        mean_absolute_dif = mean(absolute_dif),
        RMS_dif           = sqrt(mean(dif^2))
      ) %>%
      pivot_longer(
        cols      = everything(),
        names_to  = "value_type",
        values_to = "value"
      ) %>%
      mutate(
        at_tails = TRUE,
        source   = .y
      )
    
    # Combine the no-filter and filtered results:
    bind_rows(no_filter, with_filter)
  })


combined <- combined %>%
  mutate(
    value_type = factor(
      value_type,
      levels = c("mean_dif", "mean_absolute_dif", "RMS_dif"),
      labels = c("Mean difference", 
                 "Mean absolute difference", 
                 "Root mean squared difference")
    )
  )

# Create the plot
ggplot(combined, aes(x = source, y = value, fill = at_tails)) +
  geom_col(position = position_dodge()) +
  # Facet in the order set in the factor above
  facet_wrap(~ value_type, scales = "free_y") +
  labs(
    x = "Source",
    y = "Value"
  ) +
  # Use manual color scale with the requested colors
  scale_fill_manual(
    name = "At tails",
    values = c("FALSE" = "#24ff24", "TRUE" = "#490092")
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text  = element_text(face = "bold")  # emphasize facet labels
  ) + scale_y_continuous(limits = c(-1, 6))


```


### Compare prediction errors
```{r}
getNormScoreSE(norm.model, type = 1)

sim_pop_sample_with_draws %>%  
  select(age, raw_score = .prediction, .draw) %>% 
  left_join(means_sds_and_ses_RPP, by = "age") %>%
  group_by(age) %>%
  mutate(RPP_IQ_linear = iq(raw_score, RPP_mean, RPP_sd)) %>% 
  ungroup() %>% 
  group_by(.draw) %>%
    summarise(mean_prediction = mean(RPP_IQ_linear)) %>%
    summarise(RPP_SE = sd(mean_prediction)) %>% as.numeric()
```
Unclear if these values are comparable.


# Poststratification without regularisation
Weighting is often undertaken using simple averages instead of model predictions. Here we apply poststratification weights we calculated based on population data and use weights provided by TwinLife and compare the results to RPP and raw data.

## Means plot
```{r}
means_sds_and_ses_RPP <- sim_pop_sample_with_draws %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(RPP_mean = mean(mean_prediction), 
            RPP_se_of_mean = sd(mean_prediction), 
            RPP_sd = sqrt(mean(sd_prediction^2)), 
            RPP_se_of_sd = sd(sd_prediction)) 



means_sds_and_ses_tl_ps <- tl %>% 
  mutate(age = age0100) %>% 
  left_join((census %>% 
               mutate(PS_w = census_n/sum(census_n))), by = c("age", "male", "mig", "educ")) %>% 
  # set PS weights of cells that exist in the sample but not in the census to 0
  mutate(PS_w = ifelse(is.na(PS_w), 0, PS_w)) %>% 
  group_by(age) %>% 
  summarise(Raw_n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(Raw_n),
            PS_mean = weighted.mean(cft, PS_w, na.rm = T), 
            PS_sd = sqrt(weighted.mean((cft - PS_mean)^2, PS_w, na.rm = T)), 
            PS_se_of_mean = PS_sd/sqrt(Raw_n))

means_ns_sds_and_ses <- means_sds_and_ses_RPP %>% 
  left_join(means_sds_and_ses_tl_ps, by = "age")  %>%
  pivot_longer(-c(age), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")


means_ns_sds_and_ses %>% 
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(1, 4))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses 
    %>% filter(age == 65) %>% arrange(source),
    aes(label = source), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0)  +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c(
  "#7876B1FF",
  "#BC3C29FF",
  "#0072B5FF"

)) +
  labs(x = "Age", y = "Mean CFT 20-R Score")

ggsave("../04_figures/09_RPP_vs_raw_PS.png", width = 8, height = 4)
```




## Overall differences
```{r}
means_ns_sds_and_ses %>% group_by(source) %>% summarise(mean = mean(mean), se = mean(se_of_mean)) 
```

# RPP norms vs. weighted means and sds using TwinLife weights

Here we use the weights provided by the TwinLife panel study data custodians, described [here](https://pub.uni-bielefeld.de/record/2979229). We compare them with both raw  and RPP means.

## Get the design and non-response weights from the weights dataset
```{r}
tl_w_ws <- tl %>% 
  left_join((haven::read_dta("../../unshareable_data/raw/ZA6701_weights_v7-1-0.dta") %>% 
              select(c(fid, svw0100, svw0200))), by = "fid") %>% 
  # rename the weights
  mutate(dw = svw0100, # design weights
         nrw = svw0200, # non-response weights
         dnrw = svw0100*svw0200) # total weights (both weights together)
```

## Mean differences

```{r}

means_sds_and_ses_RPP <- sim_pop_sample_with_draws %>%
  group_by(age, .draw) %>% 
  summarise(mean_prediction = mean(.prediction), 
            sd_prediction = sd(.prediction)) %>%
  group_by(age) %>% 
  summarise(RPP_mean = mean(mean_prediction), 
            RPP_se_of_mean = sd(mean_prediction), 
            RPP_sd = sqrt(mean(sd_prediction^2)), 
            RPP_se_of_sd = sd(sd_prediction)) 


means_sds_and_ses_tl <- tl_w_ws %>% 
  group_by(age = age0100) %>% 
  summarise(n = n(), 
            Raw_mean = mean(cft, na.rm = T), 
            Raw_sd = sd(cft, na.rm = T), 
            Raw_se_of_mean = Raw_sd/sqrt(n),
            Design_mean = weighted.mean(cft, dw, na.rm = T), 
            Design_sd = sqrt(weighted.mean((cft - Design_mean)^2, dw, na.rm = T)), 
            Design_se_of_mean = Design_sd/sqrt(n),
            Nonresponse_mean = weighted.mean(cft, nrw, na.rm = T), 
            Nonresponse_sd = sqrt(weighted.mean((cft - Nonresponse_mean)^2, nrw, na.rm = T)), 
            Nonresponse_se_of_mean = Nonresponse_sd/sqrt(n)) 

means_ns_sds_and_ses <- means_sds_and_ses_RPP %>% 
  left_join(means_sds_and_ses_tl, by = "age") %>%
  pivot_longer(-c(age, n), names_to = c("source", ".value"), names_pattern = "([^_]*)_(.*)")

means_ns_sds_and_ses  %>%
  ggplot(aes(x = as.factor(age), y = mean, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(1, 9))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = mean - 1.96*se_of_mean, ymax = mean + 1.96*se_of_mean), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = source), family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c(
  "#7876B1FF",
  "#6F99ADFF",
  "#BC3C29FF",
  "#0072B5FF"

)) +
  labs(x = "Age", y = "Mean CFT 20-R Score")


ggsave("../04_figures/10_RPP_vs_TL.png", width = 8, height = 4)
```

No large differences to raw means.



```{r}
means_ns_sds_and_ses %>%
  group_by(source) %>% 
  summarise(mean = mean(mean), se = mean(se_of_mean))
```
Overall, non response weighting also recognised an overestimation and corrected for it, but not  as much as RPP.




## SD differences

```{r}
means_ns_sds_and_ses %>%
  ggplot(aes(x = as.factor(age), y = sd, group = source, colour = source)) +
  scale_x_discrete(breaks = seq(11, 65, by = 2),
                   expand = expansion(add = c(1, 9))) +
  geom_line(linewidth = 1) +
  geom_pointrange(shape = 18, 
                  aes(ymin = sd - 1.96*se_of_sd, ymax = sd + 1.96*se_of_sd), 
                  fatten = 3,
                  linewidth = 1,
                  position = position_dodge(width = 0.3)) +
  geom_text_repel(
    data = means_ns_sds_and_ses %>% filter(age == 65) %>% arrange(source),
    aes(label = source), 
    family = "Times", seed = 810, nudge_x = 1, hjust = 0, point.padding = 1, direction = "y") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed", size = 0.3),
    legend.position = "none"
  ) +
  scale_colour_manual(values = c(
  "#7876B1FF",
  "#6F99ADFF",
  "#BC3C29FF",
  "#0072B5FF"

)) + labs(x = "Age", y = "CFT 20-R Score SD")
```

```{r}
means_ns_sds_and_ses %>%
  group_by(source) %>% 
  summarise(sd = sqrt(mean(sd^2))) %>% 
  arrange(sd)
```

No large differences in SDs.







```{r}
sessionInfo()
```




